[1] A. Peterchev, \textbf{J. Zhang}, K. Ma, Y. Li, B. Wang, Z. Simsek, A. Vlasov, D. Murphy, M. Clinton, J. Choi (2025). Experimental Platform Utilizing Tms Waveform and Direction in Probing and Neuromodulation. Brain Stimulation: Basic, Translational, and Clinical Research in Neuromodulation Vol. 18.0 No. 1.0 pp. 312-313 Elsevier.

[2] \textbf{J. Zhang}, A. Peterchev, S. Goetz (2025). Asymmetric Modular Pulse Synthesizer: a High-power High-granularity Electronics Solution for Transcranial Magnetic Stimulation with Practically Any Pulse Shape for Neural Activation Selectivity. arXiv preprint arXiv:2503.06172    .

[3] \textbf{J. Zhang}, B. Wang, X. Tian, A. Peterchev, S. Goetz (2024). Dc-to-5-mhz Wide-output-bandwidth High-power High-fidelity Converter. IEEE Transactions on Industrial Electronics    .

[4] X. Tian, \textbf{J. Zhang}, H. Wang, S. Goetz (2024). Design and Analysis of Automatic Modulation and Demodulation Strategy in Wireless Power and Drive Transfer System. IEEE Transactions on Industrial Electronics    IEEE.

[5] \textbf{J. Zhang}, S. Goetz (2024). Direction-selective Parallel Module Structure for Cascaded Bridge and Modular Multilevel Converters with Minimum Transistor Count. IECON 2024-50th Annual Conference of the IEEE Industrial Electronics Society   pp. 1-6 IEEE.

[6] \textbf{J. Zhang}, S. Goetz (2024). A Novel Framework for Designing Asymmetrical Multilevel Circuits to Improve Fidelity and Practicality. IECON 2024-50th Annual Conference of the IEEE Industrial Electronics Society   pp. 1-6 IEEE.

[7] \textbf{J. Zhang}, B. Wang, X. Tian, A. Peterchev, S. Goetz (2024). Analytical Model and Planar Magnetic Solution for Parallelization Surges in Switched-capacitor and Series/parallel Multilevel Circuits. IEEE Transactions on Industrial Electronics    10.1109/TIE.2024.3472297.

[8] \textbf{J. Zhang}, A. Peterchev, S. Goetz (2024). Frequency-dependent Impedance Variation in Multilevel Converters with Parallel Connectivity. 2024 IEEE Applied Power Electronics Conference and Exposition (APEC)   pp. 2337-2341 IEEE.

[9] \textbf{J. Zhang}, M. Al Munefi, A. Peterchev, S. Goetz (2024). Overshoot Dynamics in Parallel Connectivity Enabled Multilevel Converters: Generalized Analytic Expression and Impact Analysis. 2024 IEEE Applied Power Electronics Conference and Exposition (APEC)   pp. 581-586 IEEE.

[10] B. Wang, \textbf{J. Zhang}, Z. Li, W. Grill, A. Peterchev, S. Goetz (2023). Optimized Monophasic Pulses with Equivalent Electric Field for Rapid-rate Transcranial Magnetic Stimulation. Journal of neural engineering Vol. 20.0 No. 3.0 pp. 036027 IOP Publishing.

[11] \textbf{J. Zhang}, Z. Li, B. Wang, A. Peterchev, S. Goetz (2023). Highly Flexible Electronics for Selective Noninvasive Stimulation Through Free Pulse Shaping in Transcranial Magnetic Stimulation and Magnetogenetics. Brain Stimulation: Basic, Translational, and Clinical Research in Neuromodulation Vol. 16.0 No. 1.0 pp. 219 Elsevier.

[12] \textbf{J. Zhang}, S. Goetz, B. Wang (2023). Gallium-nitride (gan) Transistor Design for Transient-overload Power Applications. 2023 IEEE Applied Power Electronics Conference and Exposition (APEC)   pp. 2441-2445 IEEE.

[13] B. Wang, \textbf{J. Zhang}, Z. Li, W. Grill, A. Peterchev, S. Goetz (2023). Optimized Monophasic-equivalent Transcranial Magnetic Stimulation Pulses with Reduced Coil Heating. Brain Stimulation: Basic, Translational, and Clinical Research in Neuromodulation Vol. 16.0 No. 1.0 pp. 186-187 Elsevier.

[14] \textbf{J. Zhang}, X. Tian, B. Wang, A. Peterchev, S. Goetz (2023). Modulation-enhanced Nearest-level Quantization for a Wide Output Bandwidth. IEEE Transactions on Power Electronics Vol. 39.0 No. 3.0 pp. 3289-3299 IEEE.

[15] Z. Li, \textbf{J. Zhang}, A. Peterchev, S. Goetz (2022). Modular Pulse Synthesizer for Transcranial Magnetic Stimulation with Fully Adjustable Pulse Shape and Sequence. Journal of neural engineering Vol. 19.0 No. 6.0 pp. 066015 IOP Publishing.

[16] \textbf{J. Zhang}, Y. Zhang, J. Liu, Y. Gao, X. Gao (2021). Variable Switching Frequency Scheme Minimizing Inductor Saturation Margin for Totem-pole Rectifier Based on Frequency-domain Ripple Analysis. IEEE Transactions on Industrial Electronics Vol. 69.0 No. 12.0 pp. 12632-12640 IEEE.

[17] \textbf{J. Zhang}, Y. Zhang, S. Zaman, R. Cao, X. Gao, M. Cao (2020). Precise Correction of Current Zero-crossing Distortion of Totem Pole Pfc Converter. 2020 IEEE 9th International Power Electronics and Motion Control Conference (IPEMC2020-ECCE Asia)   pp. 2414-2419 IEEE.

[18] \textbf{J. Zhang}, Y. Zhang, J. Liu (2020). Downsizing Design of Powdered Iron Core Inductor Based on Variable-frequency Modulation Targeted at Harmonics Suppression. 2020 IEEE 21st Workshop on Control and Modeling for Power Electronics (COMPEL)   pp. 1-8 IEEE.

[19] R. Cao, Y. Li, Y. Zhang, X. Liu, C. Lv, \textbf{J. Zhang} (2020). Thermal Modeling of Power Semiconductor Devices with Heat Sink Considering Ambient Temperature Dynamics. 2020 IEEE 9th International Power Electronics and Motion Control Conference (IPEMC2020-ECCE Asia)   pp. 290-295 IEEE.

[20] X. Li, Y. Zhang, P. Zeng, \textbf{J. Zhang}, J. Liu (2019). A Novel Interleaved Non-isolated Switched-capacitor Network High Step-up Dc/dc Converter. 2019 10th International Conference on Power Electronics and ECCE Asia (ICPE 2019-ECCE Asia)   pp. 2395-2401 IEEE.

[21] K. Ding, Y. Zhang, J. Liu, P. Zeng, \textbf{J. Zhang} (2018). Dynamic Performance Improvement of Bidirectional Switched-capacitor Dc/dc Converter by Right-half-plane Zero Elimination. 2018 international power electronics conference (ipec-niigata 2018-ecce Asia)   pp. 4181-4185 IEEE.